---
title: "How do recycling practices of scientific staff at ETHz differ at work versus at home?"
author:
  - name: David Zani
    orcid: 0009-0000-9673-9210
    email: dazani@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
date: "June 6, 2024"
abstract: 
  The abstract will be placed here. Breaks can be added by hitting return on the keyboard.
license: "CC BY"
citation: 
  container-title: My Blog
  url: https://www.example.com
format: html
editor: visual
csl: apa.csl
bibliography: references.bib
output:
  html_document:
    toc: true
    toc_depth: 3
---

## Introduction

3 to 5 sentences introduces the context within which the data was created.

@mcdonald2011green says stuff.

## Methods

describes in 3 to 5 sentences how the data was obtained.

## Results

```{r}
#| label: load-packages

library(tidyverse)
library(ggthemes)
library(gt)
```

Figures and tables in Results section are interpreted with 2 to 3 sentences each.

at least two data visualisations.

at least one table with summary statistics (e.g. count, mean, median, standard deviation, etc.).

## Conclusions

Conclusions concisely summarize findings in a bullet point format.

## References

includes at least 3 citations using a bibliography.bib file exported from a collection of references on Zotero.

## Running Code

See @tbl-text for data.

```{r}
#| label: tbl-text
#| tbl-cap: Some data

#head(distance_long) %>%
#  gt()

```

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
