---
title: "How do recycling practices of scientific staff at ETH Zurich differ at work versus at home?"
author:
  - name: David Zani
    orcid: 0009-0000-9673-9210
    email: dazani@ethz.ch
    affiliation: 
      - name: ETH Zurich
        url: https://ethz.ch/de.html
date: "June 6, 2024"
abstract: 
  Sustainability efforts require individuals to be aware of their waste generation and recycling practices. Literature has shown that workplace waste behavior is not well-understood. This project aims to improve the knowledge of waste generation and recycling behaviors of scientific staff members at ETH Zurich. Results indicate that scientific staff generate and recylc emore waste at home than at their place of work. No connection was found between either the waste generation amount or the proximity of recycling bins at work to the recycling frequency. Recycling bin provision may not be an effective method to increase recycling rates. Further work is needed to capture a larger number of and more diverse participants.
license: "CC BY"
format: html
editor: visual
csl: apa.csl
bibliography: references.bib
output:
  html_document:
    toc: true
    toc_depth: 3
---

## Introduction

Waste production and recycling is an important issue in global sustainability efforts. @mcdonald2011green found that Scottish commercial waste was double the domestic waste, but that workplace waste studies are less common than studies analyzing recycling at home. @oke2015workplace also found a lacking focus on at-home recycling, so they reviewed 51 previous studies to fill the gap in workplace waste streams. They found no studies in Europe outside the UK. @zotero-1430 outline the importance of organisations becoming more environmentally friendly and aware, led by programs and initiatives, but conclude "going green comes down to individual behavior" (p. 1).

Against this background, this project collects waste generation and recycling behavior data from scientific staff at universities, both at their place of work and at home, to compare the behaviors. This project was conducted as part of the lecture series "[Research Beyond the Lab](https://rbtl-fs24.github.io/website/)" at [ETH Zurich](https://ethz.ch/de.html).

## Methods

```{r}
#| echo: false
#| warning: false

library(ggplot2)
library(tidyr)
library(gt)
library(knitr)
library(forcats)
library(dplyr)

data_short <- read.csv("/cloud/project/data/processed/data_short.csv")

generation_long <- data_short %>%
  select(contains("home_generate"),
         contains("work_generate"),
         contains("work_recycle"),
         contains("home_recycle")) %>%
  mutate(id = row_number()) %>%
    filter(id != 1) %>%
  pivot_longer(cols = -id, names_to = "var", values_to = "value") %>%
  mutate(location = case_when(
    grepl("home", var) ~ "Home",
    grepl("work", var) ~ "Work")) %>%
  mutate(material = case_when(
    grepl("alu", var) ~ "Aluminum",
    grepl("pet", var) ~ "PET",
    grepl("glass", var) ~ "Glass",
    grepl("cardboard", var) ~ "Cardboard",
    grepl("paper", var) ~ "Paper",
    grepl("plastic", var) ~ "Plastic",
    grepl("electric", var) ~ "Electric",
    grepl("organic", var) ~ "Organic",
    grepl("general", var) ~ "General")) %>%
  mutate(activity = case_when(
    grepl("generate", var) ~ "generation",
    grepl("recycle", var) ~ "recycling")) %>%
  select(-var) %>%
  pivot_wider(names_from = activity, values_from = value, values_fn = list) %>%
  mutate(generation = case_when(
    generation == "Less than 1 piece" ~ "<1",
    generation == "1-2 pieces" ~ "1-2",
    generation == "3-5 pieces" ~ "3-5",
    generation == "More than 5 pieces" ~ ">5",
    generation == "Don't know" ~ "Don't know" )) %>%
  mutate(recycling = case_when(
    recycling == "Never" ~ "Never",
    recycling == "10% of the time" ~ "10%",
    recycling == "30% of the time" ~ "30%",
    recycling == "60% of the time" ~ "60%",
    recycling == "90% of the time" ~ "90%",
    recycling == "Always" ~ "Always",
    recycling == "Don't know" ~ "Don't know")) %>%
  mutate(generation = as.character(generation),
         recycling = as.character(recycling)) %>%
  mutate(generation = factor(generation, levels = c("<1", "1-2", "3-5", ">5", "Don't know")),
         recycling = factor(recycling, levels = c("Never", "10%", "30%", "60%", "90%", "Always", "Don't know")))

facility_more <- data_short %>%
  select(("work_facilities"),
         ("work_waste_knowledge"),
         ("home_waste_knowledge"),
         ("gen_more_home"),
         ("recycle_more_home")) %>%
  mutate(gen_more_home = case_when(
    gen_more_home == "TRUE" ~ "True",
    gen_more_home ==  "FALSE" ~ "False",
    TRUE ~ gen_more_home
  )) %>%
  mutate(recycle_more_home = case_when(
    recycle_more_home == "TRUE" ~ "True",
    recycle_more_home ==  "FALSE" ~ "False",
    TRUE ~ recycle_more_home
  ))
```

Data on individual waste behavior was collected through an online survey. The survey was designed to answer the specific research question "How do recycling practices of scientific staff at ETH Zurich differ at work versus at home?" The survey was emailed to 20 individuals working at ETH Zurich; `r nrow(data_short)` individuals completed the survey. The survey can be viewed [here](https://forms.gle/yrQm4BFtMCyG7k7a6).

The data was analysed using the open-source statistical software R.

## Results

@tbl-gen shows where participants thought they generated more waste. All participants stated they generated more waste at home. Only one participants responded that they produced the same amount of waste at home and at their workplace. This suggests that targeting recycling practices at home is more important when trying to improve sustainability practices.

```{r}
#| label: tbl-gen 
#| tbl-cap: Waste generation at home versus at the office  
#| warning: false


facility_more %>%
  group_by(gen_more_home) %>%
  summarise(count = n()) %>%
  mutate(gen_more_home = factor(gen_more_home,
                                levels = c("True",
                                           "False",
                                           "The same for both locations",
                                           "I don't know"))) %>%
  arrange(gen_more_home) %>%  # Arrange by the factor levels
  rename("Generate more waste at home?" = gen_more_home,
         "Answers" = count) %>%
  gt()

```

@tbl-rec shows where participants thought they recycled more waste. About half said they recycled more often at home; a quarter more at work; and a quarter recycled the same at both locations. This suggests that recycling practices at the workplace could be further improved.

```{r}
#| label: tbl-rec
#| tbl-cap: Waste recycling at home versus at the office 
#| warning: false


facility_more %>%
  group_by(recycle_more_home) %>%
  summarise(count = n()) %>%
  mutate(recycle_more_home = factor(recycle_more_home,
                                levels = c("True",
                                           "False",
                                           "The same for both locations",
                                           "I don't know"))) %>%
  arrange(recycle_more_home) %>%  # Arrange by the factor levels
  rename("Recycle more waste at home?" = recycle_more_home,
         "Answers" = count) %>%
  gt()
```

@fig-location shows the results of waste generation and recycling by material and location. It can be seen that, in general, there is no connection between how much waste participants generated and recycled. The recycling frequency varied widely among participants; for example, participants who generated 1-2 pieces of aluminum waste per day recycled anywhere from "Never" to "Always". Organic, paper, and plastic waste was generated most often, while electronic waste was generated very rarely (all participants generated less than one piece per day). Paper was the only material for which no participant stated that they never recycled it.

```{r}
#| label: fig-location
#| fig-cap: Waste generation and recycling by material and location. One piece of waste could be one aluminum can, a piece of paper, a bottle, etc.
#| warning: false
ggplot(generation_long %>% filter(!is.na(recycling)), 
       aes(x = generation, y = recycling, shape = location)) +
  geom_point(color = "black", size = 3) +
  facet_wrap(~material, ncol = 2) +
  labs(
    title = NULL,  # If you don't want a title
    x = "Generation (pieces per day)",
    y = "Recycling frequency",
    shape = "Location"
  ) +
  scale_shape_manual(values = c(1, 4)) +  # Shapes: 1 for circle, 4 for X
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false

distance_long <- data_short %>%
  select(contains("work_dist"),
         contains("work_recycle")) %>%
  mutate(id = row_number()) %>%
  pivot_longer(cols = -id, names_to = "var", values_to = "value") %>%
  mutate(material = case_when(
    grepl("alu", var) ~ "Aluminum",
    grepl("pet", var) ~ "PET",
    grepl("glass", var) ~ "Glass",
    grepl("cardboard", var) ~ "Cardboard",
    grepl("paper", var) ~ "Paper",
    grepl("plastic", var) ~ "Plastic",
    grepl("electric", var) ~ "Electric",
    grepl("organic", var) ~ "Organic",
    grepl("general", var) ~ "General")) %>%
  mutate(activity = case_when(
    grepl("dist", var) ~ "distance",
    grepl("recycle", var) ~ "recycling")) %>%
  select(-var) %>%
  pivot_wider(names_from = activity, values_from = value, values_fn = list) %>%
  mutate(recycling = case_when(
    recycling == "Never" ~ "Never",
    recycling == "10% of the time" ~ "10%",
    recycling == "30% of the time" ~ "30%",
    recycling == "60% of the time" ~ "60%",
    recycling == "90% of the time" ~ "90%",
    recycling == "Always" ~ "Always",
    recycling == "Don't know" ~ "Don't know")) %>%
  mutate(distance = as.character(distance),
         recycling = as.character(recycling)) %>%
  mutate(recycling = factor(recycling, levels = c("Never", "10%", "30%", "60%", "90%", "Always", "Don't know"))) %>%
  mutate(distance = factor(distance, levels = c("0-5 meters", "5-20 meters", "20-50 meters", "50-100 meters", "Over 100 meters", "Don't know")),
         distance = fct_recode(distance,
                               "0-5" = "0-5 meters",
                               "5-20" = "5-20 meters",
                               "20-50" = "20-50 meters",
                               "50-100" = "50-100 meters",
                               "Over 100" = "Over 100 meters",
                               "Don't know" = "Don't know")) %>%
  mutate(distance_cont = case_when(
    distance == "0-5 meters" ~ 2.5,
    distance == "5-20 meters" ~ 12.5,
    distance == "20-50 meters" ~ 35,
    distance == "50-100 meters" ~ 75,
    distance == "Over 100 meters" ~ 125,
    distance == "Don't know" ~ NA)) %>%
  mutate(recycling_cont = case_when(
    recycling == "Never" ~ 0,
    recycling == "10% of the time" ~ 10,
    recycling == "30% of the time" ~ 30,
    recycling == "60% of the time" ~ 60,
    recycling == "90% of the time" ~ 90,
    recycling == "Always" ~ 100,
    recycling == "Don't know" ~ NA))

```

@fig-distance shows the results of waste recycling by distance to the closest recycling bin. It can be seen that, in general, there is no connection between distance to a recycling bin and the recycling frequency. In other words, participants close and far from bins both recycled "Always" and "Never". The PET bin was most frequently very close to participant workplaces, while electronic waste bins were the farthest away. Only for paper waste did all participants know where the recycle bin is located.

```{r}
#| label: fig-distance
#| fig-cap: Recycling frequency by distance to bin.
#| warning: false


ggplot(distance_long %>% filter(material != "General",
                                !is.na(distance)),
       aes(x=distance, y=recycling, color = material)) +
  geom_point() +
  facet_wrap(~material, ncol = 2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, hjust = 0),
        legend.position = "none") +
  labs(
    title = NULL,  # If you don't want a title
    x = "Distance to bin (meters)",
    y = "Recycling frequency",
    color = "Material"
  )

```

## Conclusions

The main findings of this study are as follows:

-   Scientific staff generate more waste and recycle more frequently at home than at the workplace, indicating that recycling incentives should target individuals' homes before the workplace.

-   Waste generation and recycling frequency were not clearly connected, indicating that participant awareness of recycling practices are not connected to how much waste they generate.

-   Recycling frequency was not clearly connected to distance to the closest recycling bin, indicating that providing more bins may not be an efficient solution to improving recycling behavior.

These findings are qualitative in nature, as more responses would be needed for quantitative and statistically significant analyses and findings.

## References

includes at least 3 citations using a bibliography.bib file exported from a collection of references on Zotero.
